Increased Emergency Medical Response Wait Times: The Impact of Higher Call Volume and More Severe Cases Post-COVID-19

### 2024-09-27 paper/paper.qmd
Updated draft

---
title: "Emergency Medical Response in Toronto: An Analysis of Ambulance Dispatches"
author: 
  - Muhammad Abdullah Motasim
thanks: "Code and data are available at: https://github.com/abdullah-motasim/Analyzing-Ambulance-Response-Times"
date: today
date-format: long
abstract: "The Toronto Paramedic Services respond to all ambulance dispatch requests across the city. In recent years, there have been growing concerns about increased call wait times and a shortage of available ambulances. This paper analyzes the number and severity of dispatch requests over the years. Our findings indicate that longer wait times are primarily due to a higher frequency of severe emergency calls following the COVID-19 pandemic, coupled with a shortage of first responders."
format: pdf
number-sections: true
table-of-contents: true
toc-depth: 2
bibliography: references.bib
---

>>>>

---
title: "Increased Emergency Medical Response Wait Times: The Impact of Higher Call Volume and More Severe Cases Post-COVID-19"
author: 
  - Muhammad Abdullah Motasim
thanks: "Code and data are available at: https://github.com/abdullah-motasim/Analyzing-Ambulance-Response-Times"
date: today
date-format: long
abstract: "The Toronto Paramedic Services respond to all ambulance dispatch requests across the city. In recent years, there have been growing concerns about increased call wait times and a shortage of available ambulances. This paper analyzes the number and severity of dispatch requests over the years. Our findings indicate that longer wait times are primarily due to a higher frequency of severe emergency calls following the COVID-19 pandemic, coupled with a shortage of first responders."
format: pdf
number-sections: true
table-of-contents: true
toc-depth: 2
bibliography: references.bib
---
